GDPR: Is non-compliance profitable for Meta Platforms, Inc.?

### 2023-06-11 docs/research/LaTeX/research.tex
Add stock price and volume performance
Add grafana chart setup

All numerical data about \textit{Meta Platforms, Inc.} has been gathered from
the official \textit{Meta Investor Relations} website\cite{fbMetaFinancials} -
\textbf{Balance Sheets}, \textbf{Income Statements} and \textbf{Form 10-Q}.

@@

This study is approved by Fontys University of Applied Sciences, Eindhoven, The
Netherlands. All data is collected from publicly available sources and no
personal data is collected. The author is not affiliated with Meta Platforms,
Inc. or any other company mentioned in this study.

@@

asd

@@

>>>>

All numerical data about \textit{Meta Platforms, Inc.} has been gathered from
the official \textit{Meta Investor Relations} website\cite{fbMetaFinancials} -
\textbf{Balance Sheets}, \textbf{Income Statements} and \textbf{Form 10-Q}.
Stock performance data has been gathered from the official \textit{Yahoo!
Finance} website\cite{stockPrice}.

@@

This study is approved by \textit{Fontys University of Applied Sciences,
Eindhoven, The Netherlands}. All data is collected from publicly available
sources and no personal data is collected. The author is not affiliated with
\textit{Meta Platforms, Inc.} or any other company mentioned in this study.

@@

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{stock-price}
    \caption{Stock Price Performance of Meta Platforms, Inc. (META) (in
    \$)\cite{stockPrice}}
    \label{fig:stock-price}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{volume}
    \caption{Volume of Meta Platforms, Inc. (META) (in millions of
    shares)\cite{stockPrice}}
    \label{fig:volume}
\end{figure}
